A self-consistency check for unitary propagation of Hawking quanta

### 2016-11-30 Draft_BH_shells.tex
Updated appendix B

Here we will translate the coordinate quantities, $\Delta M, r_1$ and $\Delta r$, into the local physical quantities: $\sigma$ as the co-dimension-one energy density of the shell, $l$ as the physical distance from the horizon, and $\Delta l$ as the physical distance between the two shells.
This is given by the Israel Junction Condition.
\begin{equation}
	S^a_b = [K^a_b] - [K]h^a_b~.
\end{equation}
Here $K_{ab}$ is the extrinsic curvature corresponding to the induced metric.
$K = K_{ab} h^{ab}$ is the trace of the extrinsic curvature.
The middle brackets ``[ ]'' means we are calculating the extrinsic curvature from both sides of the junction and take their difference.

The induced metrics for the junction at $r_1$, expressed in the coordinate of region $I$ in Fig.\ref{fig-setup}, is the following.
\begin{equation}
	ds_{\rm induced, \ region \ I}^2 = - \left( 1 - \frac{2M}{r} \right)^{-1} dt^2 + r^2 d \Omega_2^2.	\label{13}
\end{equation}
The extrinsic curvature from this side will simply be the $r$ derivative.
Analogously we have the same induced metric written in the coordinate of region $II$,
\begin{equation}
	ds_{\rm induced, \ region \ II}^2 = - \left( 1 - \frac{2M'}{r} \right)^{-1} dt'^2 + r^2 d \Omega_2^2.	\label{14}
\end{equation}
Similarly taking the $r$ derivative here leads to the extrinsic curvature from this side.
Combine with the continuity condition that relates $t$ to $t'$, 
\begin{equation}
	dt'^2 = \left( \frac{1 - \frac{2M'}{r_1}}{ 1- \frac{2M}{r_1}} \right) dt^2~,
\end{equation}
we can calculate the extrinsic curvature components.
\begin{eqnarray}
	(K^t_t)^{I} & = & \frac{M}{r_1^2} \left( 1 - \frac{2M}{r_1} \right)^{-\frac{1}{2}} ~.	\nonumber	\\
	(K^\theta_\theta)^{I} & = & \frac{1}{r_1} \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} 
	= (K^\phi_\phi)^{I}~.	\label{16}
\end{eqnarray}
It is obvious that for region II, we simply replace $M$ by $M'$.

The time component $S^0_0$ is the surface energy density.
\begin{equation}
	\sigma = S^0_0 = \frac{1}{4 \pi r_1} \left( \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} - \left( 1 - \frac{2(M+\Delta M)}{r_1} \right)^\frac{1}{2} \right).
\end{equation}
When $2\Delta M \ll (r_1-2M)$, this is approximately given by 
\begin{eqnarray}
	\sigma  =  \frac{-1}{4 \pi r_1} \left[ \partial_X \left( 1 - \frac{2X}{r_1} \right)^\frac{1}{2} \right]_{X = M} \Delta M
	 =  \frac{\Delta M}{4 \pi r_1^2} g_{tt}^{-\frac{1}{2}}	\label{sig-Dm}
\end{eqnarray}
Next we need to replace the coordinate distance $\Delta r$ with the proper distance $\Delta l$ and the relation between them is given by
\begin{equation}
	\Delta l = \left( 1 - \frac{2M}{r_1} \right)^{-\frac{1}{2}} \Delta r = g_{tt}^{-\frac{1}{2}} \Delta r.	\label{Dl-Dr}
\end{equation}
These equations allow us to replacing $\Delta M$ by $\sigma$ and $\Delta r$ by $\Delta l$ in Eq.~(\ref{eq-result}) to get Eq.~(\ref{eq-inv}).

Finally, Eq.~(\ref{Dl-Dr}) can be integrated to give the proper distance $l$ between the inner shell and the horizon.
\begin{eqnarray}
	l & = & \int^{r_1}_{2M} \left( 1 - \frac{2M}{r} \right)^{-\frac{1}{2}} dr	\nonumber	\\
	& = & \sqrt{(r_1 - 2M)r_1} + M \log \left( \frac{ r_1 - M + \sqrt{(r_1 - 2M)r_1}}{M} \right)	~.
	\label{l-r}
\end{eqnarray}
We will be interested in two extreme cases: $M \ll l$ and $M \gg l$. The value of $l$ in these cases are given by
\begin{equation}
l \approx \begin{cases}
 r_1 - 2M & \ \ \ \ \ (M \ll l)~,	\\
 \sqrt{8M(r_1 - 2M)} & \ \ \ \ \ (M \gg l)~.
\end{cases}	
\end{equation}
This allows us to evaluate Eq.~(\ref{eq-inv}) and get Eq.~(\ref{fin-result})

>>>>

Here we will translate the coordinate quantities, $\Delta M, r_1$ and $\Delta r$, into the local physical quantities: $\sigma$ as the co-dimension-one energy density of the shell, $l$ as the physical distance from the horizon, and $\Delta l$ as the physical distance between the two shells.
This is given by the Israel Junction Condition.
\begin{equation}
	8 \pi S^a_b = [K^a_b] - [K]h^a_b~.	\label{IJC}
\end{equation}	
Here $K_{ab}$ is the extrinsic curvature corresponding to the induced metric.
$K = K_{ab} h^{ab}$ is the trace of the extrinsic curvature.
The middle brackets ``[ ]'' means we are calculating the extrinsic curvature from both sides of the junction and take their difference.

The induced metrics for the junction at $r_1$, expressed in the coordinate of region $I$ in Fig.\ref{fig-setup}, is the following.
\begin{equation}
	ds_{\rm induced, \ region \ I}^2 = h_{ab} dy^a dy^b \equiv - \left( 1 - \frac{2M}{r} \right) dt^2 + r^2 d \Omega_2^2.	\label{13}
\end{equation}

Analogously we have the same induced metric written in the coordinate of region $II$,
\begin{equation}
	ds_{\rm induced, \ region \ II}^2 = h'_{ab} dy'^a dy'^b \equiv - \left( 1 - \frac{2M'}{r} \right) dt'^2 + r^2 d \Omega_2^2.	\label{14}
\end{equation}

Matching the induced metrics at a fixed radius $r_1$ imposes the following condition.

\begin{equation}
	dt'^2 = \left( \frac{1 - \frac{2M}{r_1}}{ 1- \frac{2M'}{r_1}} \right) dt^2~,
\end{equation}

We can explicitly calculate the extrinsic curvature components.

\begin{equation}
	K_{ab} = \frac{1}{2} (\mathcal{L}_n g_{\alpha \beta}) e^\alpha_a e^\beta_b, \hspace{5mm} e^\alpha_a \equiv \frac{\partial x^\alpha}{\partial y^a},
\end{equation}
where $a,b \in \{t,\theta, \phi \}$ and $\mathcal{L}_n$ is the Lie derivative w.r.t to the normal vector $n_\alpha = g_{rr}^{-\frac{1}{2}} \partial_\alpha r = (0, g_{rr}^{-\frac{1}{2}}, 0 , 0)$. Lets look at the Lie derivative first

\begin{eqnarray}
	L_n g_{\alpha \beta} & = & n^\mu \partial_\mu g_{\alpha \beta} + \partial_\alpha n^\mu g_{\mu \beta} + \partial_\beta n^\mu g_{\alpha \mu}	\nonumber	\\
	& = & n^r \partial_r g_{\alpha \beta} + \partial_\alpha n^r g_{r \beta} + \partial_\beta n^r g_{\alpha r}	
\end{eqnarray}

Now the components of the extrinsic curvature are

\begin{equation}
	K_{ab} = \frac{1}{2} (n^r \partial_r g_{\alpha \beta} + \partial_\alpha n^r g_{r \beta} + \partial_\beta n^r g_{\alpha r}) e^\alpha_a e^\beta_b	\label{Ecuv}
\end{equation}

Notice that the since the only variable in the above equation is $r$ only the $\partial_r$ terms will contribute. Since the $a,b$ indices do not run over $r$ only the first term in the expression above will remain. Using this we can calculate the components of the extrinsic curvature.

\begin{eqnarray}
	K_{tt} & = & \frac{1}{2} (n^r \partial_r g_{tt}) 	\nonumber	\\
	& = & \frac{1}{2} \left( 1 - \frac{2M}{r} \right)^\frac{1}{2}  \left( \frac{2M}{r^2} \right)
\end{eqnarray}
and we know $(K^t_t)^{I} = g^{tt}K_{tt} = \frac{M}{r^2} \left( 1 - \frac{2M}{r} \right)^{-\frac{1}{2}}$, the $I$ index represents a quantity evaluated in the metric $I$ and similarly for $II$. The other components are

\begin{equation}
	(K^\theta_\theta)^{I} = \frac{1}{r_1} \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} = (K^\phi_\phi)^{I}.
\end{equation}
For the extrinsic curvatures in region II, we simply replace $M$ by $M'$.
\\
\\
The time component $S^t_t$ is the surface energy density can be calculated using Eq (\ref{IJC}).

\begin{eqnarray}
	\sigma = S^t_t & = & \frac{1}{8 \pi} ((K^\theta_\theta)^{I} + (K^\phi_{\phi})^{I} - (K^\phi_\phi)^{II} - (K^\theta_\theta)^{II})	\nonumber	\\
	& = & \frac{1}{4 \pi r_1} \left( \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} - \left( 1 - \frac{2M'}{r_1} \right)^\frac{1}{2} \right).
\end{eqnarray}

When $2\Delta M \ll (r_1-2M)$, this is approximately given by 
\begin{eqnarray}
	\sigma  =  -\frac{1}{4 \pi r_1} \left[ \partial_X \left( 1 - \frac{2X}{r_1} \right)^\frac{1}{2} \right]_{X = M} \Delta M
	 =  \frac{\Delta M}{4 \pi r_1^2} g_{tt}^{-\frac{1}{2}}	\label{sig-Dm}
\end{eqnarray}
Next we need to replace the coordinate distance $\Delta r$ with the proper distance $\Delta l$ and the relation between them is given by
\begin{equation}
	\Delta l = \left( 1 - \frac{2M}{r_1} \right)^{-\frac{1}{2}} \Delta r = g_{tt}^{-\frac{1}{2}} \Delta r.	\label{Dl-Dr}
\end{equation}
These equations allow us to replacing $\Delta M$ by $\sigma$ and $\Delta r$ by $\Delta l$ in Eq.~(\ref{eq-result}) to get Eq.~(\ref{eq-inv}). Finally, Eq.~(\ref{Dl-Dr}) can be integrated to give the proper distance $l$ between the inner shell and the horizon.
\begin{eqnarray}
	l & = & \int^{r_1}_{2M} \left( 1 - \frac{2M}{r} \right)^{-\frac{1}{2}} dr	\nonumber	\\
	& = & \sqrt{(r_1 - 2M)r_1} + M \log \left( \frac{ r_1 - M + \sqrt{(r_1 - 2M)r_1}}{M} \right)	~.
	\label{l-r}
\end{eqnarray}
We will be interested in two extreme cases: $M \ll l$ and $M \gg l$. The value of $l$ in these cases are given by
\begin{equation}
l \approx \begin{cases}
 r_1 - 2M & \ \ \ \ \ (M \ll l)~,	\\
 \sqrt{8M(r_1 - 2M)} & \ \ \ \ \ (M \gg l)~.
\end{cases}	
\end{equation}
This allows us to evaluate Eq.~(\ref{eq-inv}) and get Eq.~(\ref{fin-result})
